Wikipedia WALS Feature Analysis

### 2019-07-19 surprisal/MacWhinney poster/poster_plotting.Rmd
finishing touches

```{r setup, include = FALSE}
# load packages
library(knitr)
library(tidyverse)
library(directlabels)
library(tidytext)
library(tidyboot)
library(here)
library(ggthemes)
library(feather)
library(janitor)

@@

sf$Examples <- c("Noun-relative clause; relative clause-noun", 
                 "No cases; 6 cases", 
                 "SOV; VSO", 
                 "Only singular; singular and plural", 
                 "Affix; distinct word", 
                 "Prefixes; suffixes")

@@

>>>>

```{r setup, include = FALSE}
# load packages
library(knitr)
library(tidyverse)
library(directlabels)
library(tidytext)
library(tidyboot)
library(here)
library(ggthemes)
library(feather)
library(janitor)
library(gridExtra)

@@

sf$Examples <- c("Noun-RC; RC-noun", 
                 "No cases; 6 cases", 
                 "SOV; VSO", 
                 "Only singular; sing. and plural", 
                 "Affix; distinct word", 
                 "Prefixes; suffixes")

@@

```{r plotting trigram smoothing}
wiki %>% 
  mutate(Slope0 = runif(1, 0.9, 1.1)) %>% 
  mutate(Slope1 = Slope1 + Slope0) %>% 
  mutate(Slope2 = Slope2 + Slope1) %>% 
  mutate(Slope3 = Slope3 + Slope2) %>% 
  mutate(Slope4 = Slope4 + Slope3) %>% 
  mutate(Slope5 = Slope5 + Slope4) %>% 
  # rename(1 = Slope0, 2 = Slope1, 3 = Slope2, 4 = Slope3, 5 = Slope4, 6 = Slope5) %>% 
  filter(gram == "Trigram") %>% 
  select(-gram) %>% 
  sample_n(6) %>% 
  gather(position, information, -language) %>%
  ggplot(aes(x = position, y = information, group = language, color = language))  
    geom_point() + 
    geom_line() + 
    xlab("Position") + 
    ylab("Average Information") + 
    theme(axis.text.x = element_blank())
```

### 2019-07-19 surprisal/WALS_features.Rmd
finishing touches

```{r correlations}
correlation_data <- read_feather(here("Data/feature_cosine_spaces.feather"))

@@

ggplot(tidy_corr_data, aes(x = feature, y = angle, fill = gram,
                           color = gram, group = gram,
                           label = gram)) + 
  geom_smooth(method = "lm") +
  geom_jitter(alpha = .05) +
  geom_dl(method = "smart.grid") + 
  theme(legend.position = "none")

lmer(feature ~ distance * gram + (1|language1) + (1|language2),
     data = tidy_corr_data) %>%
  tidy()

>>>>

```{r correlations}
correlation_data <- read_feather(here("Data/feature_cosine_spaces.feather")) %>% 
  mutate(unigram_cosine = unigram_cosine * 180) %>% 
  mutate(trigram_cosine = trigram_cosine * 180)

@@

ggplot(tidy_corr_data, aes(x = feature, y = angle, fill = gram,
                           color = gram, group = gram,
                           label = gram)) + 
  geom_smooth(method = "lm") +
  geom_jitter(alpha = .05) +
  geom_dl(method = "smart.grid") + 
  theme(legend.position = "none") + 
  xlab("Number of WALS features in common") + 
  ylab("Information curve distance")

library(lme4)
lmer(feature ~ angle * gram + (1|language1) + (1|language2),
     data = tidy_corr_data) %>%
  tidy()
